The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-03-10 paper/forestecology.Rmd
Updated CRAN link

We address this shortcoming with the `forestecology` R package providing methods and data for forest ecology model fitting and assessment, available on CRAN (https://cran.r-project.org/web/packages/forestecology/index.html) and on GitHub (https://github.com/rudeboybert/forestecology). The package is written to model stem radial growth between two censuses based on neighborhood competition, largely following the methods in @allen_permutation_2020.

>>>>

We address this shortcoming with the `forestecology` R package providing methods and data for forest ecology model fitting and assessment, available on CRAN (https://cran.r-project.org/package=forestecology) and on GitHub (https://github.com/rudeboybert/forestecology). The package is written to model stem radial growth between two censuses based on neighborhood competition, largely following the methods in @allen_permutation_2020.
